Deep learning approaches on musical assisted-orchestration: an evaluation study

### 2020-05-07 paper/latex/paper.tex
Edit data gen section

\section{Data generation}
We used the TinySOL database to create our input data. \textbf{(Should we talk more about TinySOL here?)} When training a model, the number of samples $n$ to be used in each combination is specified. To create the training data, $n$ instruments are randomly selected from the list of specified instruments, and then a TinySOL sample is randomly selected for each chosen instrument. These samples are then combined to play simultaneously. This melspectrogram is then taken of this combinations, creating the features to be fed to the model. We created the melspectrogram by \textbf{(Alejandro can you write this of how you generated the melspectrograms using the STFT?)}

@@

Our idea is perform orchestration using deep neural networks trained for classification. By generating input data that is combinations of different instruments and pitches, the network learns how to take a sound that is a complex combination of notes and timbres and deconstruct it into its original parts. When a target sound is then fed to the network, it attempts to classify which samples are present. By taking the samples that have the highest probability of being in the target, an orchestrated solution can be created.

@@

The first deep model we tested was Convolutional Neural Network(CNN). CNN shows good performance on classification assignment for its strong ability to extract spacial features, so we implemented a basic CNN with three convolutional layers and two fully connected layers. Each convolutional layer is followed by a BatchNorm layer, a ReLU activation layer and a 2 * 2  MaxPool layer with a stride of 2. The kernel size is 3 * 3 with a stride of 1 and a padding of 1. The number of filters are 8, 16, 32. This setting is simple but we can make a good comparison between it and the baseline.

@@

@@

(Alejandro, add how there were certain instruments that performed poorly. Add how ResNet was awful for Flute and always output Flute C4)

>>>>

\section{Data generation}
We used the TinySOL database to create our input data. \textbf{(Should we talk more about TinySOL here?)}

When training a model, the number of samples $n$ to be used in each combination is specified. To create the training data, $n$ instruments are randomly selected from the list of specified instruments, and then a TinySOL sample is randomly selected for each chosen instrument. This gives $n$ different samples, each of a different intrument. These samples are combined to form a soundfile that has each sample playing simultaneously. The melspectrogram is taken of this combination, creating the features to be fed to the model. We created the melspectrogram by \textbf{(Alejandro can you write this of how you generated the melspectrograms using the STFT?)}

@@

Our idea is to perform orchestration using deep neural networks trained for classification. By generating input data that is combinations of different instruments and pitches, the network learns how to take a sound that is a complex combination of notes and timbres and deconstruct it into its original parts. When a target sound is then fed to the network, it attempts to classify which samples are present. By taking the samples that have the highest probability of being in the target, an orchestrated solution can be created.

@@

The first deep model we tested was a Convolutional Neural Network (CNN). CNN shows good performance on classification assignment for its strong ability to extract spacial features, so we implemented a basic CNN with three convolutional layers and two fully connected layers. Each convolutional layer is followed by a BatchNorm layer, a ReLU activation layer and a 2 * 2  MaxPool layer with a stride of 2. The kernel size is 3 * 3 with a stride of 1 and a padding of 1. The number of filters are 8, 16, 32. This setting is simple but we can make a good comparison between it and the baseline.

@@

\textbf{(Add results of quantitatively comparing our results to OrchIdea)}

@@

\textbf{(Alejandro, add how there were certain instruments that performed poorly. Add how ResNet was awful for Flute and always output Flute C4)}
